### 2017-07-13 Paper.tex
Updated the formulation and added the extensive formulation
Added the upper bound record and changed the solver

			& F_i^\omega, G_i^\omega \in \{0,1\} & \forall i \in I, \omega \in \Omega\\
			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J_i, \omega \in \Omega

@@

	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary (\(x\)) and continuous (\(t\)) state variables. A state variable here is a variable whose value is passed from the first stage to the second stage. Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}). However, it is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly. \textcolor{blue}{cite literature about the stochastic integer programs}. \\

@@

	Recently Zou et al. \cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables. Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts. Although this result could not be directly applied in our problem due to the continuous state variable \(t\), it provides a pivotal theoretical basis for our decomposition method.\\
	First we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}). Notice that it is difficult to directly solve the master problem because the function \(f^\omega\) is non-convex and it is hard to derive its analytical form.

@@

		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega f^\omega(x,t) & \\

@@

@@

	\textcolor{blue}{Introduce the Lagrangian cut and how it is generated.}
	Since our state variable contains both continuous variables \(t\) and binary variables \(x\), the Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed. This means that if we carry out a cutting plane scheme using the Lagrangian cuts, we will not solve the problem to the exactness but will only obtain a lower bound. \\

>>>>

			& F_i^\omega, G_i^\omega \in \{0,1\}. & \forall i \in I, \omega \in \Omega

@@

	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary (\(x\)) and continuous (\(t\)) state variables. A state variable here is a variable whose value is passed from the first stage to the second stage. Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}). \\

@@

	For our crashing optimization problem, we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}). Constraint (\ref{cons:linearCuts}) are generated by solving the sub-problems iteratively for the optimal multipliers \(\pi\) and \(\lambda\). In a regular multi-cut Benders decomposition case, the sub problem is a convex optimization problem, usually a linear program. This means a finite number of constraints on \(\theta^\omega\) can fully characterize the function \(f^\omega(x,t)\). However, in this case \(f^\omega(x,t)\) is a mixed integer linear program. It is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly. \textcolor{blue}{cite literature about the stochastic integer programs}.

@@

		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega \theta^\omega & \\

@@

		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} x_{ij} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\

@@

	Recently Zou et al. \cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables. Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts. To generate the Lagrangian multipliers, a local copy (\(\tau\) and \(z\)) of the state variable (\(\hat{t}\) and \(\hat{x}\)) is first created as in constraint (\ref{cons:local1}) and (\ref{cons:local2}) of formulation (\ref{prob:subLocal}). We can then relax the constraint (\ref{cons:local1}) and (\ref{cons:local2}) to create a Lagrangian dual problem (\ref{prob:LagDual}). The optimal solution  \(\pi^*\) and \(\lambda^*\) to the Lagrangian dual problem will be used in the Lagrangian cuts as in constraint (\ref{cons:linearCuts}). Problem (\ref{prob:LagDual}) can be solved by a subgradient method \textcolor{blue}{cite Fisher's tutorial for solving the Lagrangian Relaxation problem}.\\
		\label{prob:subLocal}
		(S^\omega_L) \quad \min \quad & t_N & \\
		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:tN}\\
		& t_i + (1-F_i) M \geq \tau_i & \forall i \in I\\
		& t_i - (1-F_i) M \leq \tau_i & \forall i \in I \\
		& x_{ij} + (1-F_i) \geq z_{ij} & \forall i \in I, j \in J_i \\
		& x_{ij} - (1-F_i) \leq z_{ij} & \forall i \in I, j \in J_i \\
		& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i \label{cons:s3}\\
		& z_{ij} = \hat{x}_{ij} & \forall i \in I, j \in J_i \label{cons:local1}\\
		& \tau_{i} = \hat{t}_{i} & \forall i \in I \label{cons:local2}\\
		& t_i \geq 0 & \forall i \in I \label{cons:tPos}\\
		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i\\
		& \tau_i \geq 0 & \forall i \in I \\
		& 0 \leq z_{ij} \leq 1 . & \forall i \in I, j \in J_i \label{cons:zRange}
		\label{prob:LagDual}
		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N - \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) - \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange})
	The result from \cite{zou2016nested} could not be directly applied in our problem since our state variable contains both continuous variables \(t\) and binary variables \(x\). The Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed. This means that if we carry out a cutting plane scheme using the Lagrangian cuts, solving the master problem (\ref{prob:master}) will only obtain a lower bound. \\
